Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/WSSSPE4_report.tex
added ORCID for KN

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: ?}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ \note{info needed}}
%
\thanks{{}$^{(12)}$ \note{info needed}}

>>>>

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ \note{info needed}}
%
\thanks{{}$^{(12)}$ \note{info needed}}
